### 2024-11-27 download-football-data.qmd
20241126 - Data Dictionary
20241127 - include postseason in download

nfl_actualStats_seasonal_team_raw <- calculate_stats(
  seasons = TRUE,
  summary_level = "season",
  stat_type = "team",
  season_type = "REG")
```

@@

save(
  nfl_actualStats_seasonal_player_raw, nfl_actualStats_seasonal_team_raw,
  file = "./data/nfl_actualStats_seasonal_raw.RData"
)
```

@@

@@

nfl_actualStats_seasonal_team <- nfl_actualStats_seasonal_team_raw %>% 
  select(season, team, everything()) %>% 
  arrange(season, team)
load(file = "./data/nfl_actualStats_seasonal.RData")
```

>>>>

nfl_actualStats_seasonal_team_raw <- calculate_stats(
  seasons = TRUE,
  summary_level = "season",
  stat_type = "team",
  season_type = "REG")

nfl_actualStats_seasonal_player_inclPost_raw <- calculate_stats(
  seasons = TRUE,
  summary_level = "season",
  season_type = "REG+POST")

nfl_actualStats_seasonal_team_inclPost_raw <- calculate_stats(
  seasons = TRUE,
  summary_level = "season",
  stat_type = "team",
  season_type = "REG+POST")
```

@@

save(
  nfl_actualStats_seasonal_player_raw, nfl_actualStats_seasonal_team_raw,
  nfl_actualStats_seasonal_player_inclPost_raw, nfl_actualStats_seasonal_team_inclPost_raw,
  file = "./data/nfl_actualStats_seasonal_raw.RData"
)
```

@@

A Data Dictionary for the variables is available in the `nfl_stats_variables` object that is returned when running the `calculate_stats()` function:

```{r}
nfl_stats_variables
```

@@

nfl_actualStats_seasonal_team <- nfl_actualStats_seasonal_team_raw %>% 
  select(season, team, everything()) %>% 
  arrange(season, team)

nfl_actualStats_seasonal_player_inclPost <- nfl_actualStats_seasonal_player_inclPost_raw %>% 
  rename(team = recent_team) %>% 
  select(player_id, season, everything()) %>% 
  arrange(player_display_name, player_id, season)

nfl_actualStats_seasonal_team_inclPost <- nfl_actualStats_seasonal_team_inclPost_raw %>% 
  select(season, team, everything()) %>% 
  arrange(season, team)
```

```{r}
nfl_actualStats_seasonal_player %>% 
  group_by(player_id, season) %>% 
  filter(n() > 1) %>% 
  head()

nfl_actualStats_seasonal_team %>% 
  group_by(team, season) %>% 
  filter(n() > 1) %>% 
  head()

nfl_actualStats_seasonal_player_inclPost %>% 
  group_by(player_id, season) %>% 
  filter(n() > 1) %>% 
  head()

nfl_actualStats_seasonal_team_inclPost %>% 
  group_by(team, season) %>% 
  filter(n() > 1) %>% 
  head()
```

save(
  nfl_actualStats_seasonal_player, nfl_actualStats_seasonal_team,
  nfl_actualStats_seasonal_player_inclPost, nfl_actualStats_seasonal_team_inclPost,
  file = "./data/nfl_actualStats_seasonal.RData"
)
```
